Beyond Adaptive Web Design

### 2014-03-18 paper/paper.tex
fix: typos

Almost every moder device contains a video camera. This is a great opportunity to introduce video motion to web applications. We can control web sites using motion gestures. We use a video camera stream and devide it into image frames. Then we can detect a website user in the each frame using a HSV filter. When we compare all pixels in two adjacent frames we get difference points. When we apply this comparision to multiple frames we can calculate a motion vector.

@@

There are many commonly used web services that produce unnecessary traffic. Elements like videos or maps are a common part of the most web sites. All of them produces many requests and the web traffic so the website user does not want to watch the video or browse the map. There are also native mobile application for that services with better perfomance which provide full user experience. So what can we to do? This is a great opportunity to utilize conditional loading to serve the best experience for the right context.

>>>>

Almost every modern device contains a video camera. This is a great opportunity to introduce video motion to web applications. We can control web sites using motion gestures. We use a video camera stream and devide it into image frames. Then we can detect a website user in the each frame using a HSV filter. When we compare all pixels in two adjacent frames we get difference points. When we apply this comparision to multiple frames we can calculate a motion vector.

@@

There are many commonly used web services that produce unnecessary traffic. Elements like videos or maps are a common part of the most web sites. All of them produce many requests and the web traffic so the website user does not want to watch the video or browse the map. There are also native mobile application for that services with better perfomance which provide full user experience. So what can we to do? This is a great opportunity to utilize conditional loading to serve the best experience for the right context.
